\section{Scope (v1.0.0) - End of 2013}
This is a short summary that shall describe the scope for the v1.0.0 BitThunder implementation.
Any requests/features required outside of this scope will have to wait for future BitThunder development
schedules. \textbf{ABSOLUTELY NO EXCEPTIONS}.

\subsection{Basic Platform Abstraction}
BitThunder will provide a mechanism to abstract the basic elements of an embedded micro-processor platform.
This will include:

\begin{itemize}
\item Single Global Machine Description / Entry point.
\item Interrupt Controller abstraction.
\item GPIO Controller abstraction.
\item System Timer Abstraction.
\end{itemize}

\subsection{Basic Device Management}
BitThunder will provide a simple mechanism for describing devices and their associated resources.
There will be a clear distinction between device description, and the associated driver required
to utilise the device. This will ensure BitThunder drivers are easily ported between platforms.

\subsubsection{Device Interfaces / APIs}
BitThunder's device manager can support any device interface, but only the following device types
will be supported in v1.0.0

\begin{itemize}
\item Interrupt controllers.
\item GPIO controllers.
\item UART devices.
\item Timer devices.
\item I2C Bus controllers.
\item CAN Bus controllers.
\item Ethernet / MAC interface controllers.
\item Basic block devices.
\item SDIO controllers.
\end{itemize}

\subsection{Core Operating System Services}
BitThunder will provide the following core operating system services.

\begin{itemize}
\item Create/Destroy processes.
\item Create/Destroy threads.
\item Basic memory manager (alloc/free).
\item Thread synchronisation objects (mutex/semaphores).
\item IPC (Inter-process communication) (message queues).
\item Virtual filesystem and basic APIs.
\item Manage volumes, partitions, and file-system mountpoints.
\item Open/Close devices.
\item Provide access to mounted filesystems and files.
\item Basic network stack and APIs.
\item High and low-resolution kernel timestamps.
\item System logging.
\item Process watchdog.
\end{itemize}

\subsection{The answer is NO!}
For clarity, and as reference for my refusal to compromise here is a quick list of items
that do not come under v1.0.0 scope. Thats not to say that BitThunder cannot or will not
support these features, simply they will not be planned until after completion of the 
v1.0.0 milestone.

\begin{itemize}
\item Real-time tracing.
\item MMU Support / Real process isolation.
\item USB (all versions) and other complex plug and play busses.
\item Support for high-level (libc based) applications. E.g. porting Samba / vi / ssh.
\end{itemize}
